CRUSE to Safe Cycling in Ireland

### 2023-09-13 paper.qmd
Add more pct refs

Commute and school travel

Other trip purposes

\[Joey please add your bit here.\]

>>>>

The methods used to generate the evidence presented in the CRUSE tool for Ireland build on previous work, particularly the Propensity to Cycle Tool (PCT), which was originally developed for the UK's Department for Transport and which is publicly available at www.pct.bike [@lovelace2017].
The PCT approach has had major policy impacts, as outlined in Research Excellence Framework (REF) impact case studies submitted by the University of Leeds and the University of Westminster, which demonstrate that the tool "revolutionised strategic cycle planning in England and Wales"[^1] by overcoming the barriers to cycling investment imposed by lack of evidence on cycling potential[^2]
.

[^1]:  See REF Impact Case Study "Cycle network policy, planning and investment transformed by the Propensity to Cycle Tool" at [results2021.ref.ac.uk](https://results2021.ref.ac.uk/impact/847d1191-7f25-46ba-a399-b481125edc8f) submitted by the University of Leeds.

[^2]:  See the REF Impact Case Study "Creating Step Changes in Cycling Policy and Infrastructure Planning across the UK" at [results2021.ref.ac.uk](https://results2021.ref.ac.uk/impact/4BBF3436-FD10-4C75-9791-F5E98AB4411B) submitted by the University of Westminster.

The first version of the PCT was based solely on current and future potential uptake of cycling for single stage travel to work at desire line, zone, route, and route network levels [@lovelace2016].
It was launched in April 2017 as the government-endorsed tool for strategic cycle network planning, as part of the Cycling and Walking Investment Strategy [@cycling2017].
Extensions of the PCT approach have included estimation of benefits at the individual level [@woodcock2018], addition of travel to school network [@goodman2019], and improvement modelling of impacts on health, environmental and distributional outcomes [@woodcock2021].
